### 2021-11-03 README.Rmd
more redirects

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Build Status](https://travis-ci.org/ropensci/EML.svg?branch=master)](https://travis-ci.org/ropensci/EML)
[![Windows build status](https://ci.appveyor.com/api/projects/status/u2gw24yfkvxgny96?svg=true)](https://ci.appveyor.com/project/cboettig/eml)
[![codecov](https://codecov.io/gh/ropensci/EML/branch/master/graph/badge.svg)](https://codecov.io/gh/ropensci/EML)
[![CRAN status](https://www.r-pkg.org/badges/version/EML)](https://cran.r-project.org/package=EML)
![downloads](http://cranlogs.r-pkg.org/badges/grand-total/RNeXML)
[![DOI](https://zenodo.org/badge/10894022.svg)](https://zenodo.org/badge/latestdoi/10894022)

@@

`EML` v2.0 is a complete re-write which aims to provide both a drop-in replacement for the higher-level functions of the existing EML package while also providing additional functionality.  This new `EML` version uses only simple and familiar list structures (S3 classes) instead of the more cumbersome use of S4 found in the original `EML`.  While the higher-level functions are identical, this makes it easier to for most users and developers to work with `eml` objects and also to write their own functions for creating and manipulating EML objects.  Under the hood, `EML` relies on the [emld](https://github.com/cboettig/emld/) package, which uses a Linked Data representation for EML.  It is this approach which lets us combine the simplicity of lists with the specificity required by the XML schema.

>>>>

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![Build Status](https://travis-ci.org/ropensci/EML.svg?branch=master)](https://travis-ci.org/ropensci/EML)
[![Windows build status](https://ci.appveyor.com/api/projects/status/u2gw24yfkvxgny96?svg=true)](https://ci.appveyor.com/project/cboettig/eml)
[![codecov](https://codecov.io/gh/ropensci/EML/branch/master/graph/badge.svg)](https://codecov.io/gh/ropensci/EML)
[![CRAN status](https://www.r-pkg.org/badges/version/EML)](https://cran.r-project.org/package=EML)
![downloads](http://cranlogs.r-pkg.org/badges/grand-total/RNeXML)
[![DOI](https://zenodo.org/badge/10894022.svg)](https://zenodo.org/badge/latestdoi/10894022)

@@

`EML` v2.0 is a complete re-write which aims to provide both a drop-in replacement for the higher-level functions of the existing EML package while also providing additional functionality.  This new `EML` version uses only simple and familiar list structures (S3 classes) instead of the more cumbersome use of S4 found in the original `EML`.  While the higher-level functions are identical, this makes it easier to for most users and developers to work with `eml` objects and also to write their own functions for creating and manipulating EML objects.  Under the hood, `EML` relies on the [emld](https://github.com/ropensci/emld/) package, which uses a Linked Data representation for EML.  It is this approach which lets us combine the simplicity of lists with the specificity required by the XML schema.
